{ \fontfamily{ptm}\selectfont Catalyst Meta Acceleration Framework: The history and the gist of it }

### 2024-11-20 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

\section{Introduction}
    \textcolor{red}{THIS REPORT IS CURRENTLY: UNFINISHED}

@@

@@

\section{Non-convex extension of Catalyst acceleration}
    The non-convex extension of Catalyst acceleration by Lin 2018 \cite{lin_catalyst_2018} is similar to the convex case in his 2015 paper \cite{lin_universal_2015}. 
    The new algorithm handles function with unknown weak convexity constant $\rho$ using a process called Auto Adapt subroutine. 
    They only claimed convergence to stationary point is claimed for the weakly convex objective. 
    \par 
    Fix $\kappa$ we use the following notations: 
    \begin{align*}
       & \mathcal M (x; y) := F(x) + \frac{\kappa}{2}\Vert x - y\Vert^2 
       \\
       & \mathcal J y := \argmin_x \mathcal M (x; y). 
    \end{align*}
    We define the algorithm and then its convergence claim below. 
    \begin{definition}[Basic 4WD Catalyst Algorithm]
        Find any $x_0 \in \text{dom}(F)$. 
        Initialize the algorithm with $\alpha_1 = 1, v_0 = x_0$. 
        For $k \ge 1$, the iterates $(x_k, y_k, v_k)$ are generated by the procedures: 
        \vspace{-0.5em}
        \begin{align*}
            &
            \textcolor{blue}{
                \text{find } \bar x_k \approx 
            }
            \argmin_{x}\left\lbrace
                    \mathcal M(x; \textcolor{violet}{x_{k - 1}})
                \right\rbrace
            \\ &\quad 
            \text{such that: }
                \text{dist}(\mathbf 0, \partial \mathcal M(\bar x_k; \textcolor{violet}{x_{k - 1}})) 
                \le 
                \kappa\Vert \textcolor{blue}{\bar x_k}- \textcolor{violet}{x_{k - 1}}\Vert, 
                \mathcal M(\textcolor{blue}{\bar x_k}; \textcolor{violet}{x_{k - 1}}) 
                \le F(\textcolor{violet}{x_{k - 1}}); 
            \\
            & y_k = \alpha_k v_{k - 1} + (1 - \alpha_k) \textcolor{violet}{x_{k - 1}};
            \\
            & 
            \textcolor{red}{\text{find }\tilde x_k \approx}
            \argmin_{x} \left\lbrace
                \mathcal M(x; y_k) 
            \right\rbrace
            \text{ such that: }
                \dist\left(
                    \mathbf 0, \partial \mathcal M(\textcolor{red}{\tilde x_k}; y_k)
                \right) 
                \le \frac{\kappa}{k + 1}\Vert \textcolor{red}{\tilde x_k} - y_k\Vert
            ;
            \\
            & v_{k} = \textcolor{violet}{x_{k - 1}} + \frac{1}{\alpha_k}(
                    \textcolor{red}{\tilde x_k} - \textcolor{violet}{x_{k - 1}}
                );
            \\
            & 
            \text{find } \alpha_{k + 1} \in (0, 1): 
            \frac{1 - \alpha_{k + 1}}{\alpha_{k + 1}^2} = \frac{1}{\alpha_k^2};
            \\
            & \text{choose } \textcolor{violet}{x_k} \text{ such that:  } 
            f(\textcolor{violet}{x_k}) = \min(f(\textcolor{blue}{\bar x_k}), f(\textcolor{red}{\tilde x_k})). 
        \end{align*}
    \end{definition}

@@

            \right)\le \phi_k^*

@@

        \end{remark}
    \subsection{Approximated Nesterov's Estimating sequence}
        In this subsection, let $\phi_k$ be the Nesterov's estimating sequence for Catalyst. 
        For all $k \ge0$, $\phi_k$ satisfies 
        \begin{align*}
            \phi_0 &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2
            \\
            \phi_k(x) &:= 
            (1 - \alpha_{k - 1})\phi_{k - 1}(x) + 
            \alpha_{k - 1}\left(
                F(x_k) + \kappa\langle y_{k - 1} - x_k, x - x_k\rangle
                + \frac{\mu}{2} \Vert x - x_k\Vert^2
            \right). 
        \end{align*}
        We prove following theorem which is Lemma A.6 in Lin's writings on Catalyst \cite{lin_universal_2015}. 
        \begin{theorem}[Canonical form of Catalyst estimating sequence]

@@

\section{Proofs for 4WD Catalyst Acceleration}
    We prove
    \hyperref[thm:basic-4wd-catalyst]{Theorem \ref*{thm:basic-4wd-catalyst}}
    in this section. 
    The lemma below characterize the lower and upper bound on the $(\alpha_k)_{k \ge 0}$ which ultimately control the convergence rate. 
    \begin{lemma}\label{app:lemma:momentum-sequence-bounds}

    \end{lemma}

>>>>

\section{Introduction}
    \textcolor{red}{THIS REPORT IS CURRENTLY: FINISHED, BUT NOT YET POLISHED}

@@

        For a detailed proofs of the estimating sequence with comparison to the accelerated proximal gradient method, see Appendix \ref*{sec:app:exct-acc-ppm}. 

@@

\section{Non-convex extension of Catalyst acceleration}\label{sec:4wd-catalyst}
    The non-convex extension of Catalyst acceleration by Lin 2018 \cite{lin_catalyst_2018} is similar to the convex case in his 2015 paper \cite{lin_universal_2015}. 
    The new algorithm handles function with unknown weak convexity constant $\rho$ using a process called Auto Adapt subroutine. 
    They only claimed convergence to stationary point is claimed for the weakly convex objective. 
    \par 
    Fix $\kappa$ we use the following notations: 
    \begin{align*}
       & \mathcal M (x; y) := F(x) + \frac{\kappa}{2}\Vert x - y\Vert^2 
       \\
       & \mathcal J y := \argmin_x \mathcal M (x; y). 
    \end{align*}
    We define the algorithm and then its convergence claim below. 
    \begin{definition}[Basic 4WD Catalyst Algorithm]\label{def:basic-4wd-catalyst}
        Find any $x_0 \in \text{dom}(F)$. 
        Initialize the algorithm with $\alpha_1 = 1, v_0 = x_0$. 
        For $k \ge 1$, the iterates $(x_k, y_k, v_k)$ are generated by the procedures: 
        \vspace{-0.5em}
        \begin{align*}
            &
            \textcolor{blue}{
                \text{find } \bar x_k \approx 
            }
            \argmin_{x}\left\lbrace
                    \mathcal M(x; \textcolor{violet}{x_{k - 1}})
                \right\rbrace
            \\ &\quad 
            \text{such that: }
                \text{dist}(\mathbf 0, \partial \mathcal M(\bar x_k; \textcolor{violet}{x_{k - 1}})) 
                \le 
                \kappa\Vert \textcolor{blue}{\bar x_k}- \textcolor{violet}{x_{k - 1}}\Vert, 
                \mathcal M(\textcolor{blue}{\bar x_k}; \textcolor{violet}{x_{k - 1}}) 
                \le F(\textcolor{violet}{x_{k - 1}}); 
            \\
            & y_k = \alpha_k v_{k - 1} + (1 - \alpha_k) \textcolor{violet}{x_{k - 1}};
            \\
            & 
            \textcolor{red}{\text{find }\tilde x_k \approx}
            \argmin_{x} \left\lbrace
                \mathcal M(x; y_k) 
            \right\rbrace
            \text{ such that: }
                \dist\left(
                    \mathbf 0, \partial \mathcal M(\textcolor{red}{\tilde x_k}; y_k)
                \right) 
                \le \frac{\kappa}{k + 1}\Vert \textcolor{red}{\tilde x_k} - y_k\Vert
            ;
            \\
            & v_{k} = \textcolor{violet}{x_{k - 1}} + \frac{1}{\alpha_k}(
                    \textcolor{red}{\tilde x_k} - \textcolor{violet}{x_{k - 1}}
                );
            \\
            & 
            \text{find } \alpha_{k + 1} \in (0, 1): 
            \frac{1 - \alpha_{k + 1}}{\alpha_{k + 1}^2} = \frac{1}{\alpha_k^2};
            \\
            & \text{choose } \textcolor{violet}{x_k} \text{ such that:  } 
            f(\textcolor{violet}{x_k}) = \min(f(\textcolor{blue}{\bar x_k}), f(\textcolor{red}{\tilde x_k})). 
        \end{align*}
    \end{definition}

@@

            &\le \phi_k^*

@@

            We are not aware of any analogous results to this theorem in the literatures.

    \subsection{Approximated Nesterov's Estimating sequence}
        In this subsection, let $\phi_k$ be the Nesterov's estimating sequence for Catalyst. 
        For all $k \ge0$, $\phi_k$ satisfies 
        \begin{align*}
            \phi_0 &:= F(x_0) + \frac{\gamma_0}{2}\Vert x - v_0\Vert^2
            \\
            \phi_k(x) &:= 
            (1 - \alpha_{k - 1})\phi_{k - 1}(x) + 
            \alpha_{k - 1}\left(
                F(x_k) + \kappa\langle y_{k - 1} - x_k, x - x_k\rangle
                + \frac{\mu}{2} \Vert x - x_k\Vert^2
            \right). 
        \end{align*}
        Observe that $\phi_k$ is a simple quadratic function. 
        We prove following theorem which is Lemma A.6 in Lin's writings on Catalyst \cite{lin_universal_2015}. 
        \begin{theorem}[Canonical form of Catalyst estimating sequence]\;\\
            Define $v_k, \gamma_k$ to be the parameters for the canonical form of $\phi_k$ as given by 
            \begin{align*}
                \phi_k^* &= \min_x \phi_k(x)
                \\
                \phi_k(x) &= \phi_k^* + \frac{\gamma_k}{2}\Vert x - v_k\Vert^2. 
            \end{align*}
            Then the parameters the canonical form $(\gamma_{k})_{k \ge0}, (v_k)_{k \ge 0}, (\phi_k^*)_{k\ge 0}$ satisfies for all $k \ge 1$
            \begin{align*}
                \gamma_k &= (1 - \alpha_{k - 1})\gamma_{k - 1} + \alpha_{k - 1}\mu, 
                \\
                v_k &= 
                \gamma_k^{-1}(
                    (1 - \alpha_{k - 1})\gamma_{k - 1}v_{k - 1}
                    + \alpha_{k - 1}\mu x_k - \alpha_{k - 1}\kappa(y_{k - 1} - x_k)
                ), 
                \\
                \phi_k^* &= (1 - \alpha_{k - 1})\phi_{k - 1}^*
                + \alpha_{k - 1}F(x_k)
                - \frac{\alpha_{k - 1}^2}{2\gamma_k}\Vert \kappa(y_{k - 1} - x_k)\Vert^2
                \\
                &\quad 
                + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
                \left(
                    \frac{\mu}{2}\Vert x_k - v_{k - 1}\Vert^2 + 
                    \langle \kappa(y_{k - 1} - x_k), v_{k - 1} - x_k\rangle
                \right). 
            \end{align*}
        \end{theorem}
        \begin{proof}
            For $v_{k + 1}$, solve for $\nabla \phi_k(v_k) = \mathbf 0$ using the recursive definition. 
            For $\gamma_k$, consider the Hessian $\nabla^2 \phi_k$ using the recursive definition. 
            The process is similar to derivations in 
            \hyperref[app:sec:thm-claim-acc-prox-grad]{Section \ref*{app:sec:thm-claim-acc-prox-grad}}.

            Next, we work on $\phi_k^*$. 
            The goal of the canonical form is to simplify the process of solving for an implicit sequence $x_k$ such that $f(x_k) \le \phi_k^*$. 
            To start consider for all $k \ge 1$: 
                \phi_k(x_k) &= 
                \phi_k^* + \frac{\gamma_k}{2}\Vert x_k - v_k\Vert^2
                & = (1 - \alpha_{k - 1})\left(
                    \phi_{k - 1}^* + \frac{\gamma_{k - 1}}{2}\Vert x_k - v_{k - 1}\Vert^2
                \right) + \alpha_{k - 1}F(x_k)
                \phi_k^* &= 
                (1 - \alpha_{k - 1})\left(
                    \phi_{k - 1}^* + \frac{\gamma_{k - 1}}{2}\Vert x_k - v_{k - 1}\Vert^2
                \right) + \alpha_{k - 1}F(x_k) - \frac{\gamma_k}{2}\Vert x_k - v_k\Vert^2
                (1 - \alpha_{k - 1})\phi_{k - 1}+ \alpha_{k - 1}F(x_k)
                \frac{(1 - \alpha_{k - 1})\gamma_{k - 1}}{2}\Vert x_k - v_{k - 1}\Vert^2
                - \frac{\gamma_k}{2}\Vert x_k - v_k\Vert^2.
                Now, it would be great to express $\Vert x_k - v_k\Vert^2$, so it depends on the iterates from previous iteration. 
                From the definition of $v_k$ we have 
                v_k - x_k &= 
                \gamma_k^{-1}(
                (
                    1 - \alpha_{k - 1})\gamma_{k - 1}v_{k - 1}
                    + \alpha_{k - 1}\mu x_k - \alpha_{k - 1}\kappa(y_{k - 1} - x_k)
                ) - x_k
                \gamma_k^{-1}(
                    (1 - \alpha_{k - 1})\gamma_{k - 1}v_{k - 1}
                    + (\alpha_{k - 1}\mu - \gamma_k) x_k - \alpha_{k - 1}\kappa(y_{k - 1} - x_k)
                \gamma_k^{-1}(
                    (1 - \alpha_{k - 1})\gamma_{k - 1}v_{k - 1}
                    - (1 - \alpha_{k - 1})\gamma_{k - 1} x_k - \alpha_{k - 1}\kappa(y_{k - 1} - x_k)
                &= \gamma_k^{-1}(
                    (1 - \alpha_{k - 1})\gamma_{k - 1}(v_{k - 1} - x_k)
                    - \alpha_{k - 1}\kappa(y_{k - 1} - x_k)
            Taking the norm and multiplying by $\gamma_k/2$ to match the terms in (eqn1) then: 
                \Vert v_k - x_k\Vert^2 &= 
                \gamma_k^{-2}\Vert (1 - \alpha_{k - 1})\gamma_{k - 1}(v_{k - 1} - x_k) \Vert^2
                \gamma_k^{-2}\Vert \alpha_{k - 1}\kappa(y_{k - 1} - x_k)\Vert^2
                - 2\gamma_k^{-2}\gamma_{k - 1}(1 - \alpha_{k - 1})\alpha_{k - 1}\langle v_{k - 1} - x_k, \kappa(y_{k - 1} - x_k) \rangle
                \frac{\gamma_k}{2}
                \Vert v_k - x_k\Vert^2 
                \frac{(1 - \alpha_{k - 1})^{2}\gamma_{k - 1}^{2}}{2\gamma_k}\Vert x_k - v_{k - 1}\Vert^2
                \frac{\alpha_{k - 1}^2}{2\gamma_k} \Vert \kappa(y_{k - 1} - x_k)\Vert^2
                    \gamma_{k - 1}(1 - \alpha_{k - 1})\alpha_{k - 1}
                }{\gamma_k}\langle v_{k - 1} - x_k, \kappa(y_{k - 1} - x_k)\rangle.  
            Substituting it back we have 
                \phi_k^* &= 
                (1 - \alpha_{k - 1})\phi_{k - 1}+ \alpha_{k - 1}F(x_k)
                \frac{(1 - \alpha_{k - 1})\gamma_{k - 1}}{2}\Vert x - v_{k - 1}\Vert^2
                \frac{(1 - \alpha_{k - 1})^{2}\gamma_{k - 1}^{2}}{2\gamma_k}\Vert x_k - v_{k - 1}\Vert^2
                    + \left(
                        \frac{\alpha_{k - 1}^2}{2\gamma_k} \Vert \kappa(y_{k - 1} - x_k)\Vert^2
                            \gamma_{k - 1}(1 - \alpha_{k - 1})\alpha_{k - 1}
                        }{\gamma_k}\langle v_{k - 1} - x_k, \kappa(y_{k - 1} - x_k)\rangle
                (1 - \alpha_{k - 1})\phi_{k - 1}+ \alpha_{k - 1}F(x_k)
                \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}\mu}{2\gamma_k}
                \Vert x_k - v_{k - 1}\Vert^2
                \frac{\alpha_{k - 1}^2}{2\gamma_k} \Vert \kappa(y_{k - 1} - x_k)\Vert^2
                &\quad + 
                \frac{\gamma_{k - 1}(1 - \alpha_{k - 1})\alpha_{k - 1}}{\gamma_k}
                \langle v_{k - 1} - x_k, \kappa(y_{k - 1} - x_k)\rangle
                (1 - \alpha_{k - 1})\phi_{k - 1} + \alpha_{k - 1}F(x_k)
                + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
                    \frac{\mu}{2}\Vert x_k - v_{k - 1}\Vert^2 
                    \langle v_{k - 1} - x_k, \kappa(y_{k - 1} - x_k) \rangle. 
            On the second equality, we made use of the following to simplify the coefficients for ${\Vert x_k - v_{k - 1}\Vert^2}$: 
                \frac{(1 - \alpha_{k - 1})\gamma_{k - 1}}{2} - 
                \frac{(1 - \alpha_{k - 1})^{2}\gamma_{k - 1}^{2}}{2\gamma_k}
                \frac{(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
                    \frac{\gamma_k}{2} - \frac{(1 - \alpha_{k - 1})\gamma_{k - 1}}{2}
                \frac{(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
                    \frac{\gamma_k - (1 - \alpha_{k - 1})\gamma_{k - 1}}{2}
                \frac{(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
                        \alpha_{k - 1}\mu
                    }{2}
            The differences of the Canonical form is cosmetic compare results from Guler, and Acceleration proximal gradient. 
            The arrangement is different because the inexact proximal inequality from \hyperref[lemma:lin-ixct-prox-ineq]{Lemma \ref*{lemma:lin-ixct-prox-ineq}} 
            are anchored on different iterates.  
    \subsection{Controlling the errors}
        The following theorem is Theorem A.8 from Lin's writing of Catalyst \cite{lin_universal_2015}. 
        It stated the propagation of errors $\epsilon_k$ from the inexact proximal inequality to the descent condition $F(x_k) \le \phi_k^*$. 
        \begin{theorem}[Controlling the error in Nesterov's estimating sequence]\;\\
            If the auxiliary sequences $v_k, y_k, \gamma_k, \alpha_k$ satisfies the conditions: 
                \gamma_k - (\kappa + \mu)\alpha_{k - 1}^2 
                &= 0
                (1 - \alpha_{k - 1})\gamma_{k - 1} + \alpha_{k - 1}\mu 
                &= (\kappa + \mu)\alpha_{k - 1}^2. 
            Then the canonical representation of estimating sequence $\phi_k^*$ and the function value 
            the inexact proximal point iterates $F(x_k)$ satisfy for all $k\ge 1$
                F(x_k) &\le \phi_k^* + \xi_k, 
                \xi_k &= 
                (1 - \alpha_{k - 1})(
                    \xi_{k - 1} + \epsilon_k 
                    - (\kappa + \mu)\langle x_k - x_k^*, x_{k - 1} - x_k\rangle
            Where we have the base case that $\xi_0 = 0$

@@

            We prove it via induction. 
            Base case is trivially satisfied via $\phi_0^* = F(x_0)$ and $\xi_0 = 0$. 
            Inductively we assume that $F(x_{k - 1}) \le \phi_{k - 1}^* + \xi_k$. 
            By definition, it means 
            \begin{align}
                \phi_{k - 1}^* &\ge 
                F(x_{k - 1}) - \xi_{k - 1} 
                \nonumber
                \langle \kappa(y_{k - 1} - x_k), x_{k - 1} - x_k\rangle
                (\kappa + \mu)\langle x_k - x_k^*, x_{k - 1} - x_k\rangle
                - \epsilon_k - \xi_{k - 1}
                \nonumber
                \langle \kappa(y_{k - 1} - x_k), x_{k - 1} - x_k\rangle
                - (1 - \alpha_{k - 1})^{-1}\xi_k. 
            \end{align}\label{app:c3-1}
            Substituting it into the canonical form representation of the estimating sequence derived from the previous section, it has 
            \begin{align}\begin{split}
                \phi_k^* &= 
                (1 - \alpha_{k - 1})\phi_{k - 1}^* 
                \alpha_{k - 1}F(x_k)
                \frac{\alpha_{k - 1}}{2\gamma_k}
                \Vert \kappa(y_{k - 1} - x_k)\Vert^2
                + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
                    \frac{\mu}{2}\Vert x_k - v_{k - 1}\Vert^2
                    + \langle \kappa(y_{k - 1} - x_k), v_{k - 1} - x_k\rangle
                (1 - \alpha_{k - 1})
                    \langle \kappa(y_{k - 1} - x_k), x_{k - 1} - x_k\rangle
                    - (1 - a_{k - 1})^{-1}\xi_k
                \alpha_{k - 1}F(x_k)
                    \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
                        \frac{\mu}{2}\Vert x_k - v_{k - 1}\Vert^2
                        + \langle \kappa(y_{k - 1} - x_k), v_{k - 1} - x_k\rangle
                    \frac{\alpha_{k - 1}}{2\gamma_k}
                    \Vert \kappa(y_{k - 1} - x_k)\Vert^2
                (1 - \alpha_{k - 1})\langle \kappa(y_{k - 1} - x_k), x_{k - 1} - x_k \rangle
                - \frac{\alpha_{k - 1}}{2\gamma_k}\Vert \kappa(y_{k - 1} - x_k)\Vert^2
                    \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{\gamma_k}
                        \frac{\mu}{2}\Vert x_k - v_{k - 1}\Vert^2
                            \kappa(y_{k - 1} - x_k), v_{k - 1} - x_k
                    \right)+ F(x_k) - \xi_k
                (1 - \alpha_{k - 1})\left\langle 
                    \kappa(y_{k - 1} - x_k), 
                        \alpha_{k - 1}\gamma_{k - 1}
                    }{
                        \gamma_k
                    }(v_{k - 1} - x_k) + x_{k - 1} - x_k
                - \frac{\alpha_{k - 1}}{2\gamma_k}\Vert \kappa(y_{k - 1} - x_k)\Vert^2
                    + \frac{\mu\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{2\gamma_k}
                    \Vert x_k - v_{k - 1}\Vert^2 + F(x_k) - \xi_k. 
                \end{split}\label{app:c3-2}\end{align}
            Next, we need to focus on the first 2 terms on the RHS
            \begin{align}
                (1 - \alpha_{k - 1})\left\langle 
                    \kappa(y_{k - 1} - x_k), 
                        \alpha_{k - 1}\gamma_{k - 1}
                    }{
                        \gamma_k
                    }(v_{k - 1} - x_k) + x_{k - 1} - x_k
                - \frac{\alpha_{k - 1}}{2\gamma_k}\Vert \kappa(y_{k - 1} - x_k)\Vert^2. 
            \end{align}\label{app:c3-3}
            The first inner product term in \ref*{app:c3-3} has
                    \kappa(y_{k - 1} - x_k),
                    x_{k - 1} - y_{k - 1} 
                    \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
                    (v_{k - 1} - y_{k - 1} + y_{k - 1} - x_k) 
                    \kappa(y_{k - 1} - x_k), 
                    x_{k - 1} - y_{k - 1}
                    \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
                    (v_{k - 1} - y_{k - 1})  
                        \kappa(y_{k - 1} - x_k), 
                        y_{k - 1} - x_k + 
                        \frac{\alpha_{k - 1}\gamma_{k - 1}}
                        {\gamma_k}
                        (y_{k - 1} - x_k)
                    \kappa(y_{k - 1} - x_k), 
                    x_{k - 1} - y_{k - 1}
                    \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
                    (v_{k - 1} - y_{k - 1})  
                    \kappa\left(
                        1 + \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
                    \Vert v_{k - 1} - y_{k - 1}\Vert^2. 
            With the above \ref*{app:c3-3} simplifies to
                (1 - \alpha_{k - 1})\left\langle 
                    \kappa(y_{k - 1} - x_k), 
                    x_{k - 1} - y_{k - 1}
                    \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
                    (v_{k - 1} - y_{k - 1})  
                    - \frac{\alpha_{k - 1}}{2\gamma_k}
                    \Vert \kappa(y_{k - 1} - x_k)\Vert^2
                    \kappa(1 - \alpha_{k - 1})\left(
                        1 + \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
                    \Vert v_{k - 1} - y_{k - 1}\Vert^2
                (1 - \alpha_{k - 1})
                    \kappa(y_{k - 1} - x_k), 
                    x_{k - 1} - y_{k - 1}
                    \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
                    (v_{k - 1} - y_{k - 1})  
                    (1 - \alpha_{k - 1})\kappa\left(
                        1 + \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
                        - \frac{\kappa\alpha_{k - 1}}{2\gamma_k}
                    \Vert y_{k - 1} - x_k\Vert^2. 
            We can simplify the coefficient of $\Vert y_{k - 1} - x_k\Vert^2$ in the above expression by the recurrence of parameter $\gamma_k$ from the canonical form of estimating sequence. 
                (1 - \alpha_k)\kappa\left(
                    1 + \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
                    - \frac{\kappa\alpha_{k - 1}}{2\gamma_k}
                \kappa\left(
                    1 - \alpha_{k - 1} + 
                    \frac{(1 - \alpha_{k - 1})\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
                    - \frac{\alpha_{k - 1}^2\kappa}{2\gamma_k}
                & \text{Use: }\gamma_k - \alpha_{k - 1}\mu = (1 - \alpha_{k - 1})\gamma_{k - 1}
                \kappa\left(
                    1 - \alpha_{k - 1} 
                    \frac{(\gamma_k - \alpha_{k - 1}\mu)\alpha_{k - 1}}{\gamma_k}
                    \frac{\alpha_{k - 1}^2\kappa}{2\gamma_k}
                &= \kappa
                    1 + 
                        -2\gamma_k\alpha_{k - 1}
                        + 2(\gamma_k - \alpha_{k - 1}\mu)\alpha_{k - 1}
                        - \alpha_{k - 1}^2\kappa
                    }{
                        2\gamma_k
                &= \kappa
                    1 + \frac{-2\alpha_{k + 1}^2\mu - \alpha_{k - 1}^2\kappa}{2\gamma_k}
                \kappa\left(
                    1 - \frac{(2\mu + \kappa)\alpha_{k - 1}^2}{2\gamma_k}
                \kappa\left(
                    1 - \frac{(\mu + \kappa/2)\alpha_{k - 1}^2}{\gamma_k}
            Now, substitute the above back to \ref*{app:c3-3} and then substitute \ref*{app:c3-3} back to \ref*{app:c3-2} to get:
                (1 - \alpha_{k - 1})
                    \kappa(y_{k - 1} - x_k), 
                    x_{k - 1} - y_{k - 1}
                    \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
                    (v_{k - 1} - y_{k - 1})  
                    \kappa\left(
                        1 - \frac{(\mu + \kappa/2)\alpha_{k - 1}^2}{\gamma_k}
                    \Vert y_{k - 1} - x_k\Vert^2
                    + \frac{\mu\alpha_{k - 1}(1 - \alpha_{k - 1})\gamma_{k - 1}}{2\gamma_k}
                    \Vert x_k - v_{k - 1}\Vert^2 + F(x_k) - \xi_k
                (1 - \alpha_{k - 1})
                    \kappa(y_{k - 1} - x_k), 
                    x_{k - 1} - y_{k - 1}
                    \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
                    (v_{k - 1} - y_{k - 1})  
                    \kappa\left(
                        1 - \frac{(\mu + \kappa/2)\alpha_{k - 1}^2}{\gamma_k}
                    \Vert y_{k - 1} - x_k\Vert^2
                    \Vert x_k - v_{k - 1}\Vert^2 + F(x_k) - \xi_k. 
            To assert the inductive hypothesis $F(x_k) \le \phi_k^*$ it's sufficient to have the inner product term equals to zero, and the coefficient of $\Vert y_k - x_k\Vert$ to be non-negative. 
            Therefore, it suffices to consider 
                x_{k - 1} - y_{k - 1}
                \frac{\alpha_{k - 1}\gamma_{k - 1}}{\gamma_k}
                (v_{k - 1} - y_{k - 1}) 
                \mathbf 0, 
                1 - \frac{(\kappa/2 + \mu)\alpha_{k - 1}^2}{\gamma_k}
                1 - (\kappa + \mu)\frac{\alpha_{k - 1}^2}{\gamma_k} 
                & \le 0. 
            In addition, if we assume equality holds then it gives: 
                \gamma_k - (\kappa + \mu)\alpha_{k - 1}^2 
                &= 0
                (1 - \alpha_{k - 1})\gamma_{k - 1} + \alpha_{k - 1}\mu 
                &= (\kappa + \mu)\alpha_{k - 1}^2. 
            For all $k \ge 1$, with vector $x_k, v_k$ and scalar $\gamma_k, \alpha_k$ given, the updates for $x_{k + 1}, y_{k + 1}, v_{k + 1}$ and $\gamma_{k + 1}$ are produced by: 
                \gamma_{k + 1} &= (1 - \alpha_{k})\gamma_k + \alpha_k \mu = (\kappa + \mu)\alpha_{k - 1}^2
                y_k &= (\gamma_k + \alpha_k \mu)^{-1}
                \tilde x_{k + 1} &\approx \mathcal J_{\kappa^{-1}} y_{k} 
                \text{ s.t: } 
                \mathcal M^{\kappa^{-1}}(x_{k + 1}, y_k) - 
                \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k} , y_k) \le \epsilon_k
                \widetilde{\mathcal G}_{\kappa^{-1}} y_k &= \kappa(y_k - \tilde x_{k + 1})
                x_{k + 1} &= y_k - \widetilde{\mathcal G}_{\kappa^{-1}} y_k
                \gamma_{k + 1}^{-1}\left(
                    (1 - \alpha_k)\gamma_k v_k + 
                    \alpha_k(\mu + \kappa)x_k 
                    - \alpha_k \kappa y_k
                &= \gamma_{k + 1}^{-1}(
                    (1 - \alpha_k)\gamma_k v_k + \alpha_k\mu x_k + 
                    \alpha_k\kappa(x_k - y_k)
                \gamma_{k + 1}^{-1}\left(
                    (1 - \alpha_k)\gamma_k v_k + \alpha_k\mu x_k - \alpha_k 
                    \widetilde{\mathcal G}_{\kappa^{-1}}y_k
            In terms of just the formatting of updates on $(v_k, y_k, x_k)$, $\alpha_k, \gamma_k$ are conducted, it's exactly the same as the Accelerated proximal gradient algorithm proved back in 
            \hyperref[app:sec:thm-claim-acc-prox-grad]{Section \ref*{app:sec:thm-claim-acc-prox-grad}}, but with $L = \kappa + \mu$ and $\tilde x_{k + 1}$ produced by the inexact proximal point instead of proximal gradient. 
            The results on the equivalent representations of the accelerated proximal gradient algorithm from the previous section will apply for this the Catalyst as well. 
            Therefore, by analysis from previous section, we also have for all $k \ge 0$: 
                y_k &= x_k + \frac{\alpha_{k - 1}(1 - \alpha_{k - 1})}{\alpha_{k - 1}^2 + \alpha_k}
                (x_k - x_{k - 1}).
            Lin's innovation of the inexact proximal inequality allows us to roll the error from the inexact proximal point into $\xi_k$ to characterize the descent of the sequence $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$. 
            It undoubtedly improved the results from Lemma 3.2 of Guler's paper in 1992 \cite{guler_new_1992}. 
